% Carlos Mecha résumé
% Last modification: 11/03/2013
% Version: 2013.1@Canada

\documentclass{template/resume}
\usepackage{contact}
\usepackage{lib/resume}

\begin{document}

\header{\name}{\email}{\address}

\titlesec{Objective}
Working in \textbf{multicultural environments}, involving numerous
resources within projects, tested my \textbf{perseverance}
and\textbf{leadership} to \textbf{react} to complicated situations,
delivering \textbf{quality}, \textbf{confidentiality} and returning the
trust given to me.

\titlesec{Technical Skills}
\begin{itemize}
  \itemsep3pt \parskip0pt \parsep1pt 
  \item Programming: Java (J2EE), C/C++, C\#, Ruby.
  \item Experience with databases: Oracle 9g, 10g, 11g, PostgreSQL, MySQL, SQLite, SQLServer.
  \item Web programming: PHP, JSP, Velocity, JavaScript (jQuery).
  \item Distributed platforms: Java RMI, CORBA, RCP.
  \item Frameworks: .NET, Struts, Jersey JAX-RS.
  \item Scripting: Bash, Perl.
  \item Programming for mobile devices: Android.
  \item Others: Lisp, Prolog, CISCO hardware, Maven2, System admin in Linux environments.
\end{itemize}

\titlesec{Experience}
\input{include/experience}  

\titlesec{Education}
\begin{itemize}
  \itemsep3pt \parskip0pt \parsep1pt
  \item 
    \education
      {2005 –- 2011}
      {Masters in Computer Science \& Engineering}
      {Carlos III University of Madrid, Spain}
      {Major in Distributed Systems. Outstanding results in databases and artificial intelligence.}
  \item 
    \education
      {2009 –- 2010}
      {Master in Information Systems Architecture}
      {National Institute of Applied Sciences, Rouen, France}
      {Exchange student.} 
\end{itemize}

\titlesec{Others}
\begin{itemize}
  \itemsep3pt \parskip0pt \parsep1pt 
  \item Language ability: English, French, Spanish and learning Japanese.
  \item Visa: \visa 
\end{itemize}

\end{document}
