% Author: Carlos Mecha

\experience
  {October 2022 - Present}
  {\href{https://rescale.com}{Rescale}, San Francisco, CA, United States}
  {Senior Software Engineering Manager}
  {\vspace{-1em}\begin{rlist}
    \item Managing an ``Unicorn team'', that accomplished everything below and kept me sane.
    \item Leading the efforts to create the next generation of Rescale Storage Devices (Cloud File System) focused on AI workloads. This project helped
    to bring multi-million contracts to Rescale.
    \item Focusing on increase the existing Storage Devices Reliability to achieve 100\% succesful operations (creating, running and maintaining
    shared filesystems) during multiple consecutive months. 
    \item Integrate Storage Devices offerings with the latest high-performance technologies like Lustre and WekaFS.
    \item Directing the team to focus on increase the capacity of our simulation outputs system to accomodate for LLMs, training
    and data-heavy operations (a.k.a. Bigger than Big Data).
    \item Owning the Incident Management Process with continuous improvements and reviews. +2,000 incidents successfully mitigated and counting.
    \item Leading the next generation of Data management and transfer components as part of Rescale Data Fabric.
    \item Creating the Rescale Data Connectors platforms from POCs, customer discovery, and general availability.
    \item Keeping COGS and OPEX always in check.
    
  \end{rlist}}

\experience
  {August 2022 - Present}
  {Mecha Engineering Services, San Francisco, CA, United States}
  {Owner and geek}
  {\vspace{-1em}\begin{rlist}
    \item Making AI projects happening.
  \end{rlist}}

\experience
  {February 2021 - August 2022}
  {\href{https://hightouch.com}{Hightouch}, San Francisco, CA, United States}
  {Engineering}
  {\vspace{-1em}\begin{rlist}
    \item Implemented the first iteration of the Destinations and Sources auto-discovery
    frameworks. This was crucial to increase the number of integrations to 60.
    \item Own enterprise-focused destinations and help 500 Fortune companies to integrate with them.
    \item Design and create a Partnerships API to integrate with other SaaS tools to
    increase user growth with minimal friction. One click, and you are in.
    \item Set the first configuration framework for infrastructure components.
  \end{rlist}}

\experience
  {April 2020 - February 2021}
  {\href{https://mapbox.com}{Mapbox}, San Francisco, CA, United States}
  {Engineering Manager}
  {\vspace{-1em}\begin{rlist}
    \item Led a group of incredible engineers on the Tilesets team. As a core product
    at Mapbox, resilience, stability and predictability were critical features the customers depend on.
    \item Involved each engineer on day-to-day management operations to ensure impact
    and visibility was always in consideration for their careers and promotions. (And convince
    a good friend Blake to become the great manager he's right now).
    \item Coordinate and monitor the relationship of our most important external vendor that
    powered our product's internal system. As a result of this proactive approach, fewer
    outages (reduced more than 50 \%) and better accountability were experienced by our customers.
    \item Honestly, one of the best teams I’ve worked with.
  \end{rlist}}


\experience
  {July 2018 - April 2020}
  {\href{https://segment.com}{Segment}, San Francisco, CA, United States}
  {Engineering Manager}
  {\vspace{-1em}\begin{rlist}
    \item Directing a team of 7 engineers, responsible for mobile, web and server-side integrations (more than 250).
    \item Providing support, growth and mentorship to the engineers in the team, from junior to tech leads.
    \item Hiring new engineers. Added 5 new engineers to the team in the last year, some of them already promoted to next levels.
    \item Shipping multi-month customer projects, coordinating Solution Architects, engineers and setting expectations, to make customers happy.
    \item Implemented a new program to include external contractors to build and maintain destinations. Positive ROI after first month.
    \item Designed a roadmap to focus on creating a platform to support external contributors and be able to scale our engineering resources
    horizontally. The first piece is described \href{https://segment.com/blog/unleashing-the-power-of-raw-data-with-amazon-lambda/}{here}.
  \end{rlist}}
  
\experience
  {February 2017 - June 2018}
  {\href{https://segment.com}{Segment}, San Francisco, CA, United States}
  {Senior Distributed Software Engineer}
  {\vspace{-1em}\begin{rlist}
    \item Improved performance of Segment's main destination router from running +10000 tasks to only 800, reducing operational
    costs and deployment risks deployments.
    \item Designed and wrote BigQuery and Snowflake warehouse connectors.
    \item As part of the Warehouses team, I was focused on design and implementing the V2 of Segment's Warehouses 
    product. Syncing currently more than 15 billion rows per day to +6000 warehouses.
    \item Helping to maintain Segment's massive AWS infrastructure (+10000 ECS tasks, +1.8PB of S3 data,
    +350 production databases, +800 EC2 instances).
    \item Pairing with the success team for technical calls with our customers. 
    \item As a side project, I optimized the warehouses dataflow, saving \$300,000 a year on AWS costs.
  \end{rlist}}

\experience
  {August 2013 - January 2017}
  {\href{https://djtechtools.com/2018/04/04/beatport-acquires-pulselocker-relaunching-subscription-service-in-q3-2018/}{Pulselocker}, San Francisco, CA, United States}
  {Software Engineer}
  {\vspace{-1em}\begin{rlist}
    \item Designed and implemented a new container-based, music ingestion engine. The engine
    synchronizes data stores like Cassandra, Couchbase, PostgreSQL, Elasticsearch and Redis.
    \item Integrating Pulselocker backend services with Celery and RabbitMQ.
    \item Helping to maintain the public API.
  \end{rlist}}

\experience
  {September 2012 - April 2014}
  {Owl-Systems, Madrid, Spain.}
  {Co-founder \& Backend Engineer}
  {\vspace{-1em}\begin{rlist}
    \item Created a management platform for educational centers, using JEE stack + Spring
    Framework and enhanced Javascript clients (HTML5 + Backbone.js).
    \item Led the Owl team to develop iOS and Android apps.
  \end{rlist}}

\experience
  {April 2012 - September 2012}
  {Lawrence Berkeley National Laboratory, Berkeley, CA, United States.}
  {Software Development Engineer}
  {\vspace{-1em}\begin{rlist}
    \item Maintained a resources management portal integrated with Atlassian Confluence,
    Google Groups, Jasper Reports and LDAP. Implemented with J2EE and JavaScript.
    \item Developed a performance management system for employees embedded into Atlassian Confluence.
  \end{rlist}}

\experience
  {November 2010 - October 2011}
  {Carlos III University of Madrid, Spain.}
  {Software Engineering Intern}
  {\vspace{-1em}\begin{rlist}
    \item Master's dissertation: Designed and developed a fully-functional distributed system
    for teachers and students of mechanical and industrial engineering. The platform provides
    remote access to laboratory hardware (motors, drills, computers, cameras, measure
    instruments, etc). Implemented using J2EE, C, Visual C++ and Android.
    \textbf{Mark: A+ with honors}
  \end{rlist}}

\experience
  {January 2010 - July 2010}
  {National Institute of Applied Sciences, Rouen, France.}
  {Software Development Intern}
  {\vspace{-1em}\begin{rlist}
    \item RDF-based Medical Database: Designed and developed a framework for a medical
    term database. We obtained a structure for quick and efficient queries applied
    to drugs, chemicals, diseases, etc. ISO9001 certified project.
    \item Taught Oracle database technologies to the students workgroup.
    \item Brain interface: Real-time analysis of EEGs for UX interaction on OpenViBE for a Digitable device.
    \item Mechatronics: PID system in a PIC16F887 for an autonomous drone.
  \end{rlist}}

\experience
  {January 2009 - July 2009}
  {Carlos III University of Madrid, Spain.}
  {Internship, network administrator}
  {\vspace{-1em}\begin{rlist}
    \item Technical support for LAN, Wi-Fi and VPN networks (approx. 5000 nodes).
  \end{rlist}}
